Auditory Scene Similarity Retrieval and Classification with Relevance based Quantization of Scattering Features

### 2016-12-12 paper/structureScene.tex
Edit methods section

%For most of the experiments reported in this paper, we will consider the DCASE2013 dataset \cite{giannoulis2013database, 7100934}. Larger datasets exists: the
%Rouen dataset \cite{rakotomamonjy2015histogram} and the public part of the DCASE2016 challenge.%
The experiments in this paper are carried out on the private part of the DCASE 2013 dataset\cite{7100934} and the public part of the DCASE 2016 dataset \cite{Mesaros2016_EUSIPCO}.

The DCASE 2013 dataset consists of two parts, namely a public and a private subset, each made up of $100$ $30$-second recordings of various acoustic scenes. The $100$ recordings are evenly divided into $10$ acoustic scene classes. To build the DCASE 2013 dataset, three different recordists visited a wide variety of locations in Greater London over a period of several months and in each scene recorded a few minutes of audio. No
systematic variations in the recordings covaried with scene
type: all recordings were made under moderate weather conditions, at varying times of day and week, and each recordist recorded each scene type. As a consequence, DCASE2013 dataset enjoys an interesting intra-class diversity while remaining manageable in terms of size, making it suitable for extensive evaluation of algorithmic design choices \cite{lagrange:hal-01082501}.

In addition, it is still a challenging dataset, with a state-of-the-art system based on feature design and SVMs achieving $76\%$ \cite{roma2013} (winner of the DCASE2013 challenge), while recent approaches based on label tree embedding achieve between $84\%$ and $87\%$ on DCASE 2013 depending on the prior knowledge used during training \cite{phan2016label}.

@@

The dataset is split into a public dataset that can used for optimizing the ASC system and a private dataset used for computing the resulting accuracy using a five-fold cross validation scheme. The folds used in this paper are the same as the ones used during the challenge.

@@

Experiments are carried out using scattering coefficients as well as mel-frequency cepstral coefficients (MFCCs) as features. For the scattering transform, each $30$-second scene is described by $128$ vectors computed with half-overlapping windows $\boldsymbol{\phi}(t)$ of duration $T=372\,\mathrm{ms}$, for a total of $24\,\mathrm{s}$. Indeed, $3$ seconds are discarded at the beginning and end of the scene to avoid boundary artifacts. Experiments are conducted with and without logarithmic compression (see Section \ref{sec:logcomp}).

MFCCs are computed for windows of $50\,\mathrm{ms}$ and hops of $25\,\mathrm{ms}$, with full frequency range. Different ranks of coefficients were tested to compute the MFCCs, results here are only reported for the best setting, which consisted of $40$ MFCCs, including the first coefficient related to the average energy. This setting gives us $600$ feature vectors per scene. To get a more robust representation, a pooling step is performed on the MFCCs: each recording is divided into $250$-second long non-overlapping ``texture'' windows \cite{1021072}, over which the feature vectors are averaged. This yields number of vectors comparable to that of the scattering transform.

@@

The influence of the temporal scattering transform and the \emph{ob} approaches are assessed in an unsupervised setting (ASSR) and in a supervised setting (ASC).

For ASSR, evaluation is performed on the private part of the DCASE 2013 dataset. The metric used is the precision at rank $k$ ($p@k$), which is computed by taking a query item and counting the number of items of the same class within the $k$ closest neighbors, and then averaging over all query items. The $p@k$ is computed for $k=\lbrace 1,\ldots,9\rbrace$, since each class only has $10$ items. Note that a $p@1$ is equivalent to the classification accuracy obtained by the classifier which chooeses the label of the closest neighbor for a given item. For each experimental setting, we only report the results obtained with the sets of parameters, \emph{i.e.} the number of clusters $M$ for the \emph{ob} approaches and the scaling parameter $k$ of the RBF kernels (see Eq. \ref{eq:kc}) leading to the best $p@9$.

@@

For ASC, the systems are again evaluated on the private part of DCASE 2013, but here with five-fold stratified cross validation. The folds are identical to those used in the original challenge. Optimal parameters (see above) are this time learned on the public part of the DCASE 2013 dataset, also using five-fold stratified cross validation.

The \emph{ob} approaches are compared to commonly used early integration approach (\emph{early}) for ASSR, while both early and late integration (\emph{late}) strategy are evaluated for the ASC setting (see Section \ref{sec:eili}).

In the same way as the majority of the DCASE2013 participants, we use an SVM for the ASC task, which is a large-margin binary discriminator with tunable regularization of misclassified examples. The parameter $C$ is here set to $1$.

For the \emph{ob} approaches, we use the precomputed kernels described in Section \ref{sec:object}. For both the \emph{early} and \emph{late} approaches, a linear kernel as well as an RBF kernel are used. As with the RBF kernels used in the \emph{ob} approaches, the RBF kernel in the SVM is scaled locally using the method proposed in \cite{selfTuneManor2004}. All feature vectors, be they frames, texture windows or centroids, are standardized prior to be given to the classifier. The standardization is computed with respect to the train/test splits of the cross validation scheme (see Section \ref{sec:stand}).

Clustering is done using $k$-means$++$ \cite{arthur2007k}, an augmented version of $k$-means with a more robust initialization procedure. Three numbers of clusters are tested: $8$, $16$ and $32$. The implementation of tte presented methods as well as the one of the experimental protocolis available\footnote{\url{https://github.com/mathieulagrange/paperStructureScene16}}.

>>>>

%For most of the experiments reported in this paper, we will consider the DCASE2013 dataset \cite{giannoulis2013database, 7100934}. Larger datasets exists: the
%Rouen dataset \cite{rakotomamonjy2015histogram} and the public part of the DCASE2016 challenge.%
The experiments in this paper are carried out on the DCASE 2013 \cite{7100934} and DCASE 2016 \cite{Mesaros2016_EUSIPCO} datasets.
The DCASE 2013 dataset consists of two parts, namely a public and a private subset, each made up of $100$ $30$-second recordings of various acoustic scenes. The $100$ recordings are evenly divided into $10$ acoustic scene classes. To build the DCASE 2013 dataset, three different recordists visited a wide variety of locations in Greater London over a period of several months and in each scene recorded a few minutes of audio. No
systematic variations in the recordings covaried with scene
type: all recordings were made under moderate weather conditions, at varying times of day and week, and each recordist recorded each scene type. As a consequence, DCASE 2013 dataset enjoys an interesting intra-class diversity while remaining manageable in terms of size, making it suitable for extensive evaluation of algorithmic design choices \cite{lagrange:hal-01082501}.
In addition, it is still a challenging dataset, with a state-of-the-art system based using handcrafted features as input to SVMs achieving $76\%$ \cite{roma2013} (winner of the DCASE2013 challenge), while recent approaches based on label tree embedding achieve between $84\%$ and $87\%$ on DCASE 2013 depending on the prior knowledge used during training \cite{phan2016label}.

@@

The public part of the dataset can used for optimizing the ASC system and the private part used for computing the resulting accuracy using a five-fold cross validation scheme. For this paper, we shall perform our experiments on the private part of the dataset. The folds used are the same as the ones used during the challenge.

The DCASE 2016 dataset has a similar organization, but here we conduct our experiments on the public part of the dataset. \ja{Any more information on this dataset?}

@@

Experiments are carried out using scattering coefficients as well as baseline mel-frequency cepstral coefficients (MFCCs) as features. For the scattering transform, each $30$-second scene is described by $128$ vectors computed with half-overlapping windows $\boldsymbol{\phi}(t)$ of duration $T=372\,\mathrm{ms}$, for a total of $24\,\mathrm{s}$. In this case, $3$ seconds are discarded at the beginning and end of the scene to avoid boundary artifacts. Experiments are conducted with and without logarithmic compression (see Section \ref{sec:logcomp}).

MFCCs are computed for windows of $50\,\mathrm{ms}$ and hops of $25\,\mathrm{ms}$, with full frequency range. The standard configuration of $39$ coefficients coupled with an average-energy measure performs best in preliminary tests, so we use this in the following. The coefficients are averaged using $250\,\mathrm{ms}$ long non-overlapping windows so that each window represents structures of similar scale to the scattering coefficients.

@@

The performance of the temporal scattering transform and the \emph{ob} approaches are assessed in an unsupervised setting (ASSR) and in a supervised setting (ASC). \ja{The \emph{ob} approaches are not really assessed for ASC, though.}

For ASSR, evaluation is performed on the private part of the DCASE 2013 dataset. The metric used is the precision at rank $k$ ($p@k$), which is computed by taking a query item and counting the number of items of the same class within the $k$ closest neighbors, and then averaging over all query items. \ja{The variable $k$ is used previously, so we should change that.} The $p@k$ is computed for $k=\lbrace 1,\ldots,9\rbrace$, since each class only has $10$ items. Note that a $p@1$ is equivalent to the classification accuracy obtained by the classifier which chooses the label of the closest neighbor for a given item. For each experimental setting, we only report the results obtained with the sets of parameters, \emph{i.e.} the number of clusters $M$ for the \emph{ob} approaches and the scaling parameter $k$ of the RBF kernels (see Eq. \ref{eq:kc}) leading to the best $p@9$. The \emph{ob} approaches are compared to commonly used early integration approach \emph{early}.

@@

For ASC, the systems are again evaluated on the private part of DCASE 2013, but here with five-fold stratified cross validation. The folds are identical to those used in the original challenge. In the same way as the majority of the DCASE 2013 participants, we use an SVM for the ASC task, which is a large-margin binary discriminator with tunable regularization of misclassified examples. The slack parameter $C$ is here set to $1$. Optimal parameters (see above) are this time learned on the public part of the DCASE 2013 dataset, also using five-fold stratified cross validation. \ja{Which parameters are these?} For these experiments, both \emph{early} and \emph{late} integration strategies are evaluated (see Section \ref{sec:eili}).

For the \emph{ob} approaches, we use the precomputed kernels described in Section \ref{sec:object}. For both the \emph{early} and \emph{late} methods, a linear kernel as well as an RBF kernel are used. As with the RBF kernels used in the \emph{ob} approaches, the RBF kernel in the SVM is scaled locally using the method proposed in \cite{selfTuneManor2004}. All feature vectors, that is scattering frames, MFCCs and centroids, are standardized prior to be given to the classifier. The standardization is computed with respect to the train/test splits of the cross validation scheme (see Section \ref{sec:stand}).

The clustering for the \emph{ob} methods is done using $k$-means$++$ \cite{arthur2007k}, an augmented version of $k$-means with a more robust initialization procedure. Three numbers of clusters are tested: $8$, $16$ and $32$. The implementation of the presented methods as well as the one of the experimental protocol is available.\footnote{\url{https://github.com/mathieulagrange/paperStructureScene16}} \ja{What is ``the one''?}
